\emph{icepack}: a new glacier flow modeling package in Python, version 1.0

### 2020-12-23 icepack.tex
Acknowledgments
Citation for MOA

\begin{figure}[h]
    \includegraphics[width=0.95\linewidth]{demos/larsen/parameter.png}
    \caption{Left: Inferred fluidity parameter $\theta$.
    Lower values indicate more deformable ice.
    Right: stream plot of ice velocity computed from this fluidity parameter.}
    \label{fig:larsen}
\end{figure}

@@

\begin{acknowledgements}
\end{acknowledgements}

>>>>

\begin{figure}[h]
    \includegraphics[width=0.95\linewidth]{demos/larsen/parameter.png}
    \caption{Left: Inferred fluidity parameter $\theta$.
    Lower values indicate more deformable ice.
    Right: stream plot of ice velocity computed from this fluidity parameter.
    Background image is the MODIS Mosaic of Antarctica \citep{scambos2007modis, haran2014modis}, courtesy of NASA NSIDC DAAC.}
    \label{fig:larsen}
\end{figure}

@@

\begin{acknowledgements}
We would like to thank the Firedrake development team for their support and for many helpful discussions.
\end{acknowledgements}
